### 2021-09-10 paper/localpsf.tex
added lemma reference

\begin{proof}
	Let
	\begin{equation*}
		X := \{v \in H^2_N(\Omega) : v(x_i) = v_i \text{ for }i=1,\dots,r\}
	\end{equation*}
	denote the feasible set for optimization problem \ref{eq:wi_optimization_problem_generic}, and let 
	\begin{equation*}
	X_0 := \{v \in H^2_N(\Omega) : v(x_i) = 0 \text{ for }i=1,\dots,r\}
	\end{equation*}	
	denote the tangent space to $X$. Note that pointwise values of functions in $H_N^2(\Omega)$ are well-defined since the Sobolev imbedding theorem (see, e.g., Theorem 7.19 in \cite{Arbogast}) implies that $H^2(\Omega)$ is continuously imbedded in the space of continuous functions $C^0(\Omega)$ when $d < 4$, and we are considering $d \in \{1,2,3\}$. The feasible set $X$ is therefore a closed affine subspace of $H^2_N(\Omega)$, the tangent space $X_0$ is a closed subspace of $H^2_N(\Omega)$, and optimization problem \ref{eq:wi_optimization_problem_generic} is well-defined.

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_*(x_i) = f_i$ for $i=1,\dots,r$. We have
	\begin{align*}
	v_*(x_i) &= \beta + \sum_{j=1}^r c_j \theta_j(x_i) \\
	&= \beta + \sum_{j=1}^r c_j \left(\psi_i, \Delta \theta_j\right)_{L^2(\Omega)} + \avg\left(\theta_j\right) \\
	&= \beta + \sum_{j=1}^r c_j \left(\psi_i, \psi_j\right)_{L^2(\Omega)} \\
	&= \beta + \sum_{j=1}^r c_j S_{ij}
	\end{align*}
	In the first line we used the definition of $v_*$ in \eqref{eq:optimal_v}. In the second line we used Lemma LEM. In the third line we used the facts that, by construction, $\Delta \theta_j = \psi_j$ and $\int_\Omega \theta_j(x) dx = 0$. In the fourth line we used the definition of $S$ in \eqref{eq:S_matrix}. Hence the condition $v_*(x_i) = f_i$ for $i=1,\dots,r$ may be written in matrix form as
	\begin{equation*}
	S \mathbf{c} + \beta \mathbf{1} = \mathbf{f},
	\end{equation*}
	and this must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\mathbf{c}$ and $\beta$. So $v_* \in X$.

@@

	\paragraph{Variational equation} To show that $v_*$ satiafies variational equation \eqref{eq:variational_up}, notice that
	\begin{align*}
	(\Delta v_*, \Delta p)_{L^2(\Omega)} =& \sum_{i=1}^r c_i(\Delta \theta_i, \Delta p)_{L^2(\Omega)} \\
	=& \sum_{i=1}^r c_i \left(p(x_i) + \avg\left(p\right)\right) \\
	=& \avg\left(p\right) \sum_{i=1}^r c_i. 
	\end{align*}
	In the first line we used the definition of $\theta_i$ and the fact that the Laplacian of a constant is zero. In the second line we used Lemma LEM. In the third line we used the fact that $p(x_i)=0$ because $p \in X_0$. Hence variational equation \eqref{eq:variational_up} holds if $\sum_{i=1}^r c_i = 0$, which may be written in matrix form as $\mathbf{1}^T \mathbf{c} = 0$. This must hold because it is the second block row in system \eqref{eq:interpolation_linear_system}.
\end{proof}

>>>>

\begin{proof}
	Let
	\begin{equation*}
		X := \{v \in H^2_N(\Omega) : v(x_i) = v_i \text{ for }i=1,\dots,r\}
	\end{equation*}
	denote the feasible set for optimization problem \ref{eq:wi_optimization_problem_generic}, and let 
	\begin{equation*}
	X_0 := \{v \in H^2_N(\Omega) : v(x_i) = 0 \text{ for }i=1,\dots,r\}
	\end{equation*}	
	denote the tangent space to $X$. Note that pointwise values of functions in $H_N^2(\Omega)$ are well-defined since the Sobolev imbedding theorem (see, e.g., Theorem 7.19 in \cite{Arbogast}) implies that $H^2(\Omega)$ is continuously imbedded in the space of continuous functions $C^0(\Omega)$ when $d < 4$, and we are considering $d \in \{1,2,3\}$. The feasible set $X$ is therefore a closed affine subspace of $H^2_N(\Omega)$, the tangent space $X_0$ is a closed subspace of $H^2_N(\Omega)$, and optimization problem \eqref{eq:wi_optimization_problem_generic} is well-defined.

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_*(x_i) = f_i$ for $i=1,\dots,r$. We have
	\begin{align*}
	v_*(x_i) &= \beta + \sum_{j=1}^r c_j \theta_j(x_i) \\
	&= \beta + \sum_{j=1}^r c_j \left(\psi_i, \Delta \theta_j\right)_{L^2(\Omega)} + \avg\left(\theta_j\right) \\
	&= \beta + \sum_{j=1}^r c_j \left(\psi_i, \psi_j\right)_{L^2(\Omega)} \\
	&= \beta + \sum_{j=1}^r c_j S_{ij}
	\end{align*}
	In the first line we used the definition of $v_*$ in \eqref{eq:optimal_v}. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the facts that, by construction, $\Delta \theta_j = \psi_j$ and $\int_\Omega \theta_j(x) dx = 0$. In the fourth line we used the definition of $S$ in \eqref{eq:S_matrix}. Hence the condition $v_*(x_i) = f_i$ for $i=1,\dots,r$ may be written in matrix form as
	\begin{equation*}
	S \mathbf{c} + \beta \mathbf{1} = \mathbf{f},
	\end{equation*}
	and this must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\mathbf{c}$ and $\beta$. So $v_* \in X$.

@@

	\paragraph{Variational equation} To show that $v_*$ satiafies variational equation \eqref{eq:variational_up}, notice that
	\begin{align*}
	(\Delta v_*, \Delta p)_{L^2(\Omega)} =& \sum_{i=1}^r c_i(\Delta \theta_i, \Delta p)_{L^2(\Omega)} \\
	=& \sum_{i=1}^r c_i \left(p(x_i) - \avg\left(p\right)\right) \\
	=& -\avg\left(p\right) \sum_{i=1}^r c_i. 
	\end{align*}
	In the first line we used the definition of $\theta_i$ and the fact that the Laplacian of a constant is zero. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the fact that $p(x_i)=0$ because $p \in X_0$. Hence variational equation \eqref{eq:variational_up} holds if $\sum_{i=1}^r c_i = 0$, which may be written in matrix form as $\mathbf{1}^T \mathbf{c} = 0$. This must hold because it is the second block row in system \eqref{eq:interpolation_linear_system}.
\end{proof}
